Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-20 eswc-2012/phdsymp.tex
differences in query times
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@109 43ef1190-90fd-4dd7-a769-d0121f02b80e

In many cases, this is sufficient. Sometimes, one engine can execute a
query in an order of magnitude faster than another, in which case, there
is hardly reasonable doubt as to which is faster. Small differences may seem
unimportant but may become important if they are systematic. Even if
one engine is dramatically better than another in one case, small
deficiencies may add up to make the other a better choice for most
applications anyway.

@@

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires it.

>>>>

In many cases, this is sufficient. Sometimes, one engine can execute a
query in an order of magnitude faster than another. If this happens
systematically for many different queries, there is hardly reasonable
doubt as to which is faster. In most cases, the query response times
differs little, however. Small differences may seem unimportant
but may become important if they are systematic. Even if one engine is
dramatically better than another in one case, small deficiencies may
add up to make the other a better choice for most applications anyway.

@@

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires such a benchmark.
